Bow shocks, bow waves, and dust waves

### 2018-06-05 papers/Papers1234/sec-dust-bow-intro.tex
Make a start on the back reaction section

Further restrictions on the existence of dust waves arise when the
effects of magnetic fields are considered, as will be discussed in
\S~\ref{sec:magn-effects-grain} below.

@@

>>>>

The combined effects of the three conditions are illustrated in
Figure~\ref{fig:existence-dust-wave} for each of the three example
main sequence stars from Table~\ref{tab:stars}.  Further restrictions
on the existence of dust waves arise when the effects of magnetic
fields are considered, as will be discussed in
\S~\ref{sec:magn-effects-grain} below.

@@

So far we have ignored the effect of the drag force on the gas stream
itself, but it is clear that this must become important as \(\tau_*\)
approaches \(\tau_{*,\text{max}})\), since that is the point where the
dust wave transitions to a bow wave, in which the dust and gas are
perfectly coupled.  A full treatment of this problem would require
solving the hydrodynamic equations simultaneously with the equations
of motion of the dust grains, which is beyond the scope of this paper.
Instead, we outline a heuristic approach that qualitatively captures
the physics involved.

The maximum drag force experienced by a grain is at the rip point.
Since the grain follows a zero-net-force phase track up until that
point, this can be written with the help of
equations~(\ref{eq:dust-rad-force}, \ref{eq:dust-r0}) as
\begin{equation}
  \label{eq:fdrag-max}
  f\drag (R_\dag) = f\rad(R_\dag) =   \frac{m\grain v_\infty^2 R\starstar}{ 2 R_\dag^2} 
\end{equation}
The timescale of the flow can be characterized by the crossing time
\(R_\dag / v_\infty\), but the residence time of the grain at the bow apex
will be several times larger than this (see previous section).  On the
other hand, the average drag force during this residence will be
several times smaller than the \(f\drag (R_\dag)\).  Therefore, we introduce a dimensionless factor, \(\alpha\), which we expect to be of order unity, and write the total impulse imparted to the grain by drag as
\begin{equation}
  \label{eq:grain-impulse}
  J\drag = \alpha f\drag (R_\dag) \frac{R_\dag}{v_\infty}
  = \tfrac12 \alpha m\grain v_\infty \frac{R\starstar}{R_\dag} \ .
\end{equation}
